Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2018-08-16 article.Rnw
Correct the curves of the restriction

myreg <- colorRampPalette(c("gray90",  "gray20"))
xy1 <- levelplot(emu ~ phi + mu, data = grid,
                 aspect = "fill",
                 col.regions = myreg,
                 xlab = expression(phi),
                 ylab = expression(mu),
                 sub = "(a)",
                 colorkey = list(space = "top"),
                 par.settings = ps2,
                 panel = function(x, y, z, ...) {
                     panel.levelplot(x, y, z, ...)
                     panel.curve(10 - ( exp(x) - 1)/(2 * exp(x)),
                                 lty = 2)
                     panel.abline(v = 0, lty = 2)
                 })

xy2 <- levelplot(eva ~ phi + mu, data = grid,
                 aspect = "fill",
                 col.regions = myreg,
                 xlab = expression(phi),
                 ylab = expression(mu),
                 sub = "(b)",
                 colorkey = list(space = "top"),
                 par.settings = ps2,
                 panel = function(x, y, z, ...) {
                     panel.levelplot(x, y, z, ...)
                     panel.curve((10 - ( exp(x) - 1)/
                                  (2 * exp(x)))/exp(x), lty = 2)
                     panel.abline(v = 0, lty = 2)
                 })

>>>>

myreg <- colorRampPalette(c("gray90",  "gray20"))
xy1 <- levelplot(emu ~ phi + mu, data = grid,
                 aspect = "fill",
                 col.regions = myreg,
                 xlab = expression(phi),
                 ylab = expression(mu),
                 sub = "(a)",
                 colorkey = list(space = "top"),
                 par.settings = ps2,
                 panel = function(x, y, z, ...) {
                     panel.levelplot(x, y, z, ...)
                     panel.curve(10 - (exp(x) - 1)/(2 * exp(x)),
                                 lty = 2)
                     panel.abline(v = 0, lty = 2)
                 })

xy2 <- levelplot(eva ~ phi + mu, data = grid,
                 aspect = "fill",
                 col.regions = myreg,
                 xlab = expression(phi),
                 ylab = expression(mu),
                 sub = "(b)",
                 colorkey = list(space = "top"),
                 par.settings = ps2,
                 panel = function(x, y, z, ...) {
                     panel.levelplot(x, y, z, ...)
                     panel.curve(10 - (exp(x) - 1)/(2 * exp(x)),
                                 lty = 2)
                     panel.abline(v = 0, lty = 2)
                 })
